Pre-processing high frequency animal tracking data

### 2020-09-30 05_calibration_data.Rmd
add some figures

# remove speed outliers
data <- atl_filter_covariates(data = data,
            filters = c("(speed_in < 20 & speed_out < 20)"))

@@

# use only residence or walking points
data <- data[residence == T | tID == "walking", ]
```

@@

# on data where the residence is unknown
patch_res_unknown <- atl_res_patch(data, 
                                buffer_radius = 10,
                                lim_spat_indep = 100,
                                lim_time_indep = 30,
                                min_fixes = 3)
```

@@

```{r}
# all patch figures
fig_patches <- mapply(function(raw_data, patch_sf, patch_summary) {
  ggplot()+
    geom_point(data = raw_data,
               aes(x, y, col = residence),
               size = 0.1)+
    geom_sf(data = patch_sf,
            fill = "yellow", col = "black",
            alpha = 0.5)+
    geom_segment(data = patch_summary,
              aes(x = shift(x_end, type = "lead"), 
                  y = shift(y_end, type = "lead"),
                  xend = shift(x_start), yend = shift(y_start)),
              col = "blue", size = 1)+
    scale_colour_manual(values = c("red", "blue"))+
    ggthemes::theme_map()
}, list(data_res, data), patch_sf_data, patch_summary_data,
SIMPLIFY = FALSE)

# patch with residence points and walking patches
fig_basic_residence <-
  ggplot()+
  geom_point(data = data,
             aes(x, y,
                 col = residence),
            size = ifelse(data$residence, 4, 0.2),
            shape = ifelse(data$residence, 2, 1),
            show.legend = FALSE)+
  scico::scale_color_scico_d(palette = "berlin",
                             direction = -1,
                             begin = 0.2, end = 0.8)+
  ggthemes::theme_map()

# figure of residence patches known
fig_patch_known <- 
  ggplot()+
  geom_sf(data = patch_sf_data[[1]],
          fill = "steelblue", col = NA)+
  geom_path(data = patch_summary_data[[1]],
            aes(x_median, y_median),
            col = "red", size = 0.2)+
  ggthemes::theme_map()

# figure of unknown patches
fig_patch_unknown <- 
  ggplot()+
  geom_sf(data = patch_sf_data[[2]],
          fill = "steelblue", col = NA)+
  geom_path(data = patch_summary_data[[2]],
            aes(x_median, y_median),
            col = "red", size = 0.2)+
    ggthemes::theme_map()

@@

# save figure
ggsave(fig_res_patch, filename = "figures/fig_calib_respatch.png",
       height = 185/25, width = 185/25)
```

>>>>

# remove speed outliers
data <- atl_filter_covariates(data = data,
            filters = c("(speed_in < 15.7 & speed_out < 15.7)"))

@@

# get a simple inverse of speed as residence time classification
data_slow <- copy(data_raw)
data_slow <- data_slow[speed_in < 1, ]
```

@@

# on data where the residence is unknown
patch_res_unknown <- atl_res_patch(data_slow, 
                                buffer_radius = 10,
                                lim_spat_indep = 100,
                                lim_time_indep = 30,
                                min_fixes = 10)
```

@@

```{r}
# patch with residence points and walking patches
fig_basic_residence <-
  ggplot()+
  geom_point(data = data,
             aes(x, y,
                 col = residence),
            size = ifelse(data$residence, 4, 0.2),
            shape = ifelse(data$residence, 2, 1),
            show.legend = FALSE)+
  scico::scale_color_scico_d(palette = "berlin",
                             direction = -1,
                             begin = 0.2, end = 0.8)+
  ggthemes::theme_map()

# figure of residence patches known
fig_patch_known <- 
  ggplot()+
  geom_sf(data = patch_sf_data[[1]],
          fill = "steelblue", col = NA)+
  geom_path(data = patch_summary_data[[1]],
            aes(x_median, y_median),
            col = "red")+
  ggthemes::theme_map()

# figure of unknown patches
fig_patch_unknown <-
  ggplot()+
  geom_path(data = patch_summary_data[[1]],
            aes(x_median, y_median),
            col = "black", size = 0.2, lty = 2)+
  geom_sf(data = patch_sf_data[[2]],
          fill = "steelblue", col = NA)+
  geom_segment(data = patch_summary_data[[2]],
               aes(x = x_end,
                   xend = shift(x_start, type = "lead"),
                   y = y_end,
                   yend = shift(y_start, type = "lead")),
               col = "red"
  )+
  ggthemes::theme_map()

@@

# save figure
ggsave(fig_res_patch, filename = "figures/fig_calib_respatch.png",
       height = 200/25, width = 185/25)
```

## Compare patch metrics

### Compare known patches

```{r}
# get known patch summary
patch_summary_real <- data_res[, list(nfixes_real = .N,
                                      x_median = round(median(x), digits = -2),
                                      y_median = round(median(y), digits = -2),
                                      duration_real = as.numeric(
                                        max(time) - min(time))), 
                               by = "tID"]

# round median coordinate for inferred patches
patch_summary_inferred <- 
        patch_summary_data[[1]][, 
                                c("x_median", "y_median", 
                                  "nfixes", "duration")
                                ][, `:=`(x_median = round(x_median, digits = -2),
                                         y_median = round(y_median, digits = -2))]

# join with respatch summary
patch_summary_compare <- 
  merge(patch_summary_real,
        patch_summary_inferred, 
        on = c("x_median", "y_median"),
        all.x = TRUE, all.y = TRUE)
```

### Plot known and unknown patches

```{r}
# make figure comparing different methods
ggplot()+
  geom_point(data = patch_summary_compare,
             aes(nfixes_real, 
                 nfixes),
             show.legend = F,
            size = 4,
            shape = 1)+
  geom_smooth(data = patch_summary_compare,
             aes(nfixes_real, 
                 nfixes),
             show.legend = F)+
  scale_x_log10()+
  scale_y_log10()+
  coord_cartesian(xlim = c(10, NA))+
  ggthemes::theme_few()+
  labs(x = "# positions (real)",
       y = "# positions (inferred)")
```
